Hypertension and microbiome

### 2020-02-06 articletwo.Rmd
Wrong panel order

>>>>

Listing Lactobacillus spp

```{r write supplement}
lactobacilli.names.incols <- pseq.species %>%
    taxa %>%
    mygrep(word = "^Lactobacillus.*Bacteria") %>%
    renametaxa %>%
    sort %>%
    list.partition(parts = 4) %>%
    mycbind %>%
    as.data.frame

lactobacilli.names.flextable <- flextable(lactobacilli.names.incols) %>%
    flextable::fontsize(size = 10, part = "header") %>%
    flextable::fontsize(size = 10, part = "body") %>%
    flextable::width(j=1:3, width = 1.8) %>%
    flextable::align(align = "left", part = "header") %>%
    flextable::align(align = "left")

lactobacilli.names.flextable 
```
